Integrated multi-omics analysis reveals Lactobacillus anti-inflammatory process in vaginal tissue

### 2021-03-11 reports/rmarkdown/01_data_pre_processing.Rmd
Changes to run on Vildes computer

---
title: "`r params$project_title`"
editor_options:
  chunk_output_type: console
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  pdf_document:
    toc: yes
  html_document:
    code_folding: hide
    toc: yes
    toc_float:
      collapsed: no
params:
  organisation: Karolinska Institutet
  pi_mail: prin.cipal@ki.se
  pi_name: Prin Cipal
  project_title: Broliden_5325
  redmine_issue: '#5325'
  requester_mail: kristina.broliden@ki.se
  requester_name: Kristina Broliden
  staff_mail: supp.ortstaff@nbis.se
  staff_name: Supp Ortstaff
  staff_web: https://nbis.se/about/staff/supp-ortstaff/
---

@@

```{r, echo = FALSE}
PATH <- "~/Desktop/NBIS/SMS_Projects/broliden_5325/data/" #Path to the data

@@

# Extract taxonomic information to file
taxa_info <- lapply(dataset_names, function(x){
  x <- read.csv( paste0(PATH,"/",x))
  temp <- as.matrix(x[,c((ncol(x)-6):ncol(x))])
  temp[is.na(temp)] <- "NA"
  return(t(temp))
})
taxa_info <- t(as.data.frame(taxa_info))
rownames(taxa_info) <- sub("other.","other ",rownames(taxa_info))
rownames(taxa_info) <- sub("[.][0123456789","other ",rownames(taxa_info))
sps <- apply( taxa_info[,6:7] ,1,function(x) paste(x,collapse ="_"))
not_complete <- grepl("_NA",sps)
taxa <- apply( taxa_info ,1,function(x) paste(x,collapse ="_"))
taxa[not_complete] <- sub("_NA.*","",taxa[not_complete])
taxa[not_complete] <- sub(".*_","other ",taxa[not_complete])
taxa[!not_complete] <- sps[!not_complete]
taxa <- sub("_"," ",taxa)
use <- !is.na(taxa) & (taxa != "NA")
taxa[taxa == "NA"] <- "other"
rownames(taxa_info) <- taxa
taxa_info <- taxa_info[! duplicated(rownames(taxa_info)),]
write.csv2(taxa_info, paste0(PATH,"../results/taxonomy.csv"),row.names = T)
```

@@

```{r, echo = FALSE}
trx <- read.csv(paste0(PATH,"/TRX_rawcounts.csv"),row.names = 1)
trx <- rowsum(trx[,-c(1,2)],trx$symbol)
colnames(trx) <- sub("ML","",colnames(trx))
trx  <- trx[ rownames(trx) != "" , ]
colnames(trx) <- as.character(metadata$ID)[ match(colnames(trx) , as.character(metadata$PatID) ) ]
trx <- trx[ rowSums(trx > 5) >= 3 , ]
trx <- t( log2( t( trx ) / colSums(trx) * 1e6 + 1 ) )
write.csv( trx , paste0(PATH,"../results/Tissue_RNAseq_V3_normalized.csv"),row.names = T )
```

>>>>

---
title: "`r params$project_title`"
editor_options:
  chunk_output_type: console
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  #pdf_document:
    #toc: yes
  html_document:
    code_folding: hide
    toc: yes
    toc_float:
      collapsed: no
params:
  organisation: Karolinska Institutet
  pi_mail: prin.cipal@ki.se
  pi_name: Prin Cipal
  project_title: Broliden_5325
  redmine_issue: '#5325'
  requester_mail: kristina.broliden@ki.se
  requester_name: Kristina Broliden
  staff_mail: supp.ortstaff@nbis.se
  staff_name: Supp Ortstaff
  staff_web: https://nbis.se/about/staff/supp-ortstaff/
---

@@

```{r, echo = FALSE}
PATH <- "~/Desktop/NBIS/SMS_Projects/broliden_5325/data/" #Path to the data
PATH <- "../../data/" #Path to the data

@@

# Extract taxonomic information to file
taxa_info <- lapply(dataset_names, function(x){
  x <- read.csv( paste0(PATH,"/",x))
  temp <- as.matrix(x[,c((ncol(x)-6):ncol(x))])
  temp[is.na(temp)] <- "NA"
  return(t(temp))
})
taxa_info <- t(as.data.frame(taxa_info))
rownames(taxa_info) <- sub("other.","other ",rownames(taxa_info))
rownames(taxa_info) <- sub("[.][0123456789]","other ",rownames(taxa_info))
sps <- apply( taxa_info[,6:7] ,1,function(x) paste(x,collapse ="_"))
not_complete <- grepl("_NA",sps)
taxa <- apply( taxa_info ,1,function(x) paste(x,collapse ="_"))
taxa[not_complete] <- sub("_NA.*","",taxa[not_complete])
taxa[not_complete] <- sub(".*_","other ",taxa[not_complete])
taxa[!not_complete] <- sps[!not_complete]
taxa <- sub("_"," ",taxa)
use <- !is.na(taxa) & (taxa != "NA")
taxa[taxa == "NA"] <- "other"
rownames(taxa_info) <- taxa
taxa_info <- taxa_info[! duplicated(rownames(taxa_info)),]
write.csv2(taxa_info, paste0(PATH,"../results/taxonomy.csv"),row.names = T)
```

@@

```{r, echo = FALSE}
trx <- read.csv(paste0(PATH,"/TRX_rawcounts.csv"),row.names = 1)
trx <- rowsum(trx[,-c(1,2)],trx$symbol)
colnames(trx) <- sub("ML","",colnames(trx))
trx  <- trx[ rownames(trx) != "" , ]
trx  <- trx[ rownames(trx) != "NA" , ]
colnames(trx) <- as.character(metadata$ID)[ match(colnames(trx) , as.character(metadata$PatID) ) ]
trx <- trx[ rowSums(trx > 5) >= 3 , ]
trx <- t( log2( t( trx ) / colSums(trx) * 1e6 + 1 ) )
write.csv( trx , paste0(PATH,"../results/Tissue_RNAseq_V3_normalized.csv"),row.names = T )
```

### 2021-03-11 reports/rmarkdown/03_integrated_datasets.Rmd
Changes to run on Vildes computer

```{r, echo = FALSE}
groupings <- lapply( names(datasets_all_samples)[-1] ,function(x){
  x <- read.csv2( paste0(PATH,"results/Sample_Louvain_clusters_",x,".csv"),row.names = 1 ) })
names(groupings) <- names(datasets_all_samples)[-1]
all_names <- unique(unlist(lapply(groupings,function(x)rownames(x))))

>>>>

```{r eval=FALSE, include=FALSE}
groupings <- lapply( names(datasets_all_samples)[-1] ,function(x){
  x <- read.csv2( paste0(PATH,"results/Sample_Louvain_clusters_",x,".csv"),row.names = 1 ) })
names(groupings) <- names(datasets_all_samples)[-1]
all_names <- unique(unlist(lapply(groupings,function(x)rownames(x))))

### 2021-03-11 reports/rmarkdown/manuscript/manuscript_template.Rmd
Changes to run on Vildes computer

#################################
# COHORT SCHEMATIC ILLUSTRATION #
#################################
par(mar=c(0,0,0,0))
fig1a <- magick::image_read("schematics.pdf",density = 900)
plot(c(0,1),c(0,1),axes=F,type="n",xlab="",ylab="",xaxs="i",yaxs="i")
rasterImage(fig1a, 0, 0, 1, 1)

>>>>

#################################
# COHORT SCHEMATIC ILLUSTRATION #
#################################
par(mar=c(0,0,0,0))
#fig1a <- magick::image_read("schematics.pdf",density = 900)
plot(c(0,1),c(0,1),axes=F,type="n",xlab="",ylab="",xaxs="i",yaxs="i")
#rasterImage(fig1a, 0, 0, 1, 1)
